\thetitle

### 2021-05-07 paper/paper.tex
explanation setups

\MS[t]{ideas: Similar Selçuk (2013) detect that a high update frequency has a negative effect and
  thus should be reduced. They conclude that the lead times ought to control the WIP level, instead
  of the due date reliability as changes are directly seen (Knollmann and Windt, 2013). For a review
  of analytical works in the context of the LTS see Bendul and Knollmann (2016).}

@@

\paragraph{Medium Variability.} The results for medium variability in the system are presented in
Table~\ref{tbl:unif}, where a uniform demand interarrival time is used.

  % a discount factor of \(0.99\).
  %    demandUnif65_145            -- 90%   -- 6.
  % -- demandUnif78_158 -- 80%   -- 3.
  % -- demandUnif95_175  -- 70%   -- 1.
  % -- demandExp105  -- 90%           -- 5.
  % -- demandExp118  -- 80%          -- 4.
  % -- demandExp135  -- 70%          -- 2.

\MS[t]{Exp - Exp in simulation model?}

@@

    distributed demand interarrival times.\newline \(^{1,2}\) Costs marked with the same number are

@@

    distributed interarrival times of the demand.\newline \(^{1,2,3}\) Costs with the same number are

>>>>

% \MS[t]{ideas: Similar Selçuk (2013) detect that a high update frequency has a negative effect and
%   thus should be reduced. They conclude that the lead times ought to control the WIP level, instead
%   of the due date reliability as changes are directly seen (Knollmann and Windt, 2013). For a review
%   of analytical works in the context of the LTS see Bendul and Knollmann (2016).}

@@

\paragraph{Medium Variability.} The results for medium variability in the system are presented in
Table~\ref{tbl:unif}, where a uniform demand interarrival time is used. We use the tuples
\(70-\Unif\), \(80-\Unif\), and \(90-\Unif\) to indicate the experimental setup of using uniform
demand interarrival times with a aimed bottleneck utilisation of \(70\%\), \(80\%\), or \(90\%\)
respectively. The results state the accumulated costs, averaged over all replications, for the work
in process (WIPC), the finished goods inventory (FGIC), the backorder costs (BOC), as well as the
sum of the finished good inventory and backorder costs (FGIC+BOC) and the sum over all three cost
centers (SUM). For a better insight in the timing performance we also provide the average shopfloor
throughput time (SFTT), i.e.\@ the average time an order spends in the system after being released
and until reaching the finished goods inventory, the finished goods inventory time (FGIT), as well
as the service level (SL). The later is given in percentage and states the percentage of orders that
were produced on time. Finally, the actual measured costs per period (Cost.p.P) and the by the
algorithm learned average reward \(\avgrew\) are stated. The tested methods are the deep Q-Learning
algorithm with discount factor \(0.99\) (\(\ql{0.99}\)), the \ARA{} algorithm with discount factors
\(0.99\) (\(\rl{0.99}\)) and \(1.00\) (\(\rl{1.00}\)), as well as the backward infinite loading
technique \BIL{} with fixed lead times between \(1\) and \(4\) as indicated by the number
($\BILOne$-$\BILFour$).

For the case of medium variability with a utilisation of \(70\%\) we can see that

  % a discount factor of \(0.99\).
  %    demandUnif65_145            -- 90%   -- 6.
  % -- demandUnif78_158 -- 80%   -- 3.
  % -- demandUnif95_175  -- 70%   -- 1.
  % -- demandExp105  -- 90%           -- 5.
  % -- demandExp118  -- 80%          -- 4.
  % -- demandExp135  -- 70%          -- 2.

@@

    distributed demand interarrival times. \(^{1,2}\) Costs marked with the same number are

@@

    distributed interarrival times of the demand. \(^{1,2,3}\) Costs with the same number are
